Blue Hunters: Bluetooth RSSI Locator Robots

### 2018-02-01 article/article.tex
delete unnecessary stuff

\hypertarget{video}{%
\subsubsection{Video}\label{video}}

@@

\hypertarget{ieee-code-of-ethics}{%
\subsubsection{IEEE Code of Ethics}\label{ieee-code-of-ethics}}

Our project, as well as the design and creation project thereof, adheres
to the \href{https://www.ieee.org/about/ethics.html}{IEEE Code of
Ethics}. The project itself is relatively small and physically
self-contained; it did not have any immediate impact on the environment
or safety and health of potential users, we the creators, or any others.
We chose the project's topic out of interest and for a challenge,
without any conflict of interest. Our report is honest and realistic;
none of our data is fabricated, and our conclusions reflect our hard
findings. We did not accept any form of bribery.

The project investigated the use of an emerging and popular technology
(BLE) in a new application (distance sensing). We consistently received
and built upon advice from our TAs and professor Bruce Land, and cite
the work we used in the basis of our project.

Additionally, neither we nor our project presented any act of
discrimination, and our project does not injure others in any way. We
assisted our colleagues (both fellow group members and other classmates)
when the occasion arose, such as by offering help debugging or lending a
spare module before a demo.

Overall, our project complies with the IEEE Policies, 7.8 Code of
Ethics.

@@

\hypertarget{appendix-a-legal-considerations}{%
\subsubsection{Appendix A: Legal
Considerations}\label{appendix-a-legal-considerations}}

\begin{itemize}
\tightlist
\item
  The group approves this report for inclusion on the course website.
\item
  The group approves the video for inclusion on the course youtube
  channel.
\item
  The TI CC2541 meets FCC CFR47 Part 15 requirements. \footnote{See the
    top of page 8 of \url{http://www.ti.com/lit/ds/symlink/cc2541.pdf}
    for compliance information.}
\end{itemize}

\hypertarget{appendix-b-source-listing}{%
\subsubsection{Appendix B: Source
Listing}\label{appendix-b-source-listing}}

Our source code can be found
\href{https://github.com/orangeturtle739/bluehunters}{on Github}. Each
file can also be found below:

\hypertarget{code}{%
\paragraph{Code}\label{code}}

\begin{itemize}
\tightlist
\item
  \href{generated/ble.c.html}{\texttt{ble.c}}
\item
  \href{generated/ble.h.html}{\texttt{ble.h}}
\item
  \href{generated/imu.c.html}{\texttt{imu.c}}
\item
  \href{generated/imu.h.html}{\texttt{imu.h}}
\item
  \href{generated/servo.c.html}{\texttt{servo.c}}
\item
  \href{generated/servo.h.html}{\texttt{servo.h}}
\item
  \href{generated/pt_cornell_1_2_2.c.html}{\texttt{pt\_cornell\_1\_2\_2.c}}
\item
  \href{generated/pt_cornell_1_2_2.h.html}{\texttt{pt\_cornell\_1\_2\_2.h}}
\item
  \href{generated/main.c.html}{\texttt{main.c}}
\item
  \href{generated/main.h.html}{\texttt{main.h}}
\item
  \href{generated/config_1_2_2.h.html}{\texttt{config\_1\_2\_2.h}}
\end{itemize}

\hypertarget{cad}{%
\paragraph{CAD}\label{cad}}

\hypertarget{sources}{%
\subparagraph{Sources}\label{sources}}

\begin{itemize}
\tightlist
\item
  \href{generated/main.scad.html}{\texttt{main.scad}}
\item
  \href{generated/frame.scad.html}{\texttt{frame.scad}}
\item
  \href{generated/wheel.scad.html}{\texttt{wheel.scad}}
\item
  \href{generated/drag.scad.html}{\texttt{drag.scad}}
\item
  \href{generated/concept.scad.html}{\texttt{concept.scad}}
\end{itemize}

\hypertarget{stl}{%
\subparagraph{STL}\label{stl}}

\begin{itemize}
\tightlist
\item
  \href{stl/frame.stl}{\texttt{frame.stl}}
\item
  \href{stl/wheel.stl}{\texttt{wheel.stl}}
\item
  \href{stl/drag.stl}{\texttt{drag.stl}}
\end{itemize}

@@

\hypertarget{appendix-c-schematics}{%
\subsubsection{Appendix C: Schematics}\label{appendix-c-schematics}}

@@

\hypertarget{appendix-e-work-distribution}{%
\subsubsection{Appendix E: Work
Distribution}\label{appendix-e-work-distribution}}

\begin{itemize}
\tightlist
\item
  \textbf{Jacob:}

  \begin{itemize}
  \tightlist
  \item
    Bluetooth firmware hacking
  \item
    Bluetooth UART code
  \item
    CAD design \& 3D printing
  \end{itemize}
\item
  \textbf{Jane:}

  \begin{itemize}
  \tightlist
  \item
    I2C IMU code
  \item
    Robot motion code and gradient descent algorithm
  \end{itemize}
\item
  \textbf{Justin:}

  \begin{itemize}
  \tightlist
  \item
    Servo control code
  \item
    Board assembly (3 small boards and our 3 of our protoboards)
  \item
    Schematic
  \end{itemize}
\end{itemize}

>>>>

@@

@@

\hypertarget{appendix-c-schematics}{%
\subsubsection{Appendix A: Data}\label{appendix-c-schematics}}

@@

\hypertarget{appendix-c-schematics}{%
\subsubsection{Appendix B: Schematics}\label{appendix-c-schematics}}

@@
